---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Draft Proposal

## Preamble

This document is a draft proposal. It has no formal status and is subject
to change. It has not been submitted.

## Scope

*TODO* Add some introduction on Graphics or Grammar and ggplot2

Proposed scope: "CRAN packages self-identifying as ggplot2 extensions"
To be decided: "Alternatives to ggplot2 for implementing Graphics of Grammar"

## Related CRAN Task Views

*TODO*
[Dynamic Visualizations](https://cran.r-project.org/web/views/DynamicVisualizations.html)

*TODO* The following Task View is not on CRAN. Check with maintainers to assert the current status.
[Static Visualizations](https://github.com/dicook/ctv-staticvisualizations/blob/main/StaticVisualizations.md)

## Packages

For now, the code below is used to create a list of packages that extend
ggplot2:

```{r list-gg-extensions, warning=FALSE, message=FALSE}
library(dplyr)
library(httr2)
library(readr)
library(stringr)
library(yaml)
library(tools)

gg_pkgs_cran <-
  CRAN_package_db() |> 
  filter(
    str_detect(Package, "^gg|^GG|gg$|GG$"),
    str_detect(Depends, "ggplot2") | str_detect(Imports, "ggplot2")
  )

gg_pkgs_gallery <-
  "https://raw.githubusercontent.com/ggplot2-exts/gallery/refs/heads/gh-pages/_config.yml" |>
  request() |>
  req_perform() |>
  resp_body_string() |>
  (\(x) read_yaml(text = x))()

gg_pkgs_gallery <-
  gg_pkgs_gallery$widgets |>
  bind_rows()

gg_pkg_joined <-
  full_join(
    x  = gg_pkgs_cran,
    y  = gg_pkgs_gallery,
    by = c(Package = "name")
  )

write_csv(gg_pkg_joined, "gg-pkgs.csv")
```

We need to think of a way of presenting the list of packages: which are
core packages?; what is a good way to present the packages in a structured
manner?

## Maintainers

In no particular order:

 * <https://github.com/EvaMaeRey>
 * <https://github.com/jtr13>
 * <https://github.com/pepijn-devries>

This is a preliminary list of maintainers.
